First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q^{2}

### 2019-11-12 MY_PUBLICATIONS/PRL/body.tex
updated

in the regions in which there is an overlap in $p_{r}$. \\
\indent Below $p_{r}\sim 300$ MeV/c, both Hall A and C data agree well with all theoretical models, as FSIs and other non-cucleonic 
\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\

@@

\begin{figure}[bh!]
\includegraphics[scale=0.5]{prl_plots/PRL_plot1.pdf}
\caption{The reduced cross section $\sigma_{red}(p_{r})$ as a function of neutron recoil momentum $p_{r}$ is shown in (a)-(c) for recoil angles \\  $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively,
with a bin width of $\pm 5^{o}$. The data is compared to the previous Hall A experiment results as well as the Paris, AV18 and CD-Bonn theoretical reduced cross sections.}
\label{fig:fig2}
\end{figure}
\newpage
\twocolumngrid
%\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\

>>>>

in the regions in which they overlap in $p_{r}$. \\
\indent At larger neutron recoil angles of $\theta_{nq}\sim75^{o}$ [Fig. \hyperref[fig:fig2]{2(c)}], the data follows the CD-Bonn PWIA (momentum distributions) up to $p_{r}\sim $100 MeV/c, and at $p_{r}\gtrsim$300 MeV/c, the FSIs become the dominat process and exhibit a
characteristic ``flattening'' (smaller falloff) with $p_{r}$. This behaviour of FSI with larger recoil angles was predicted by the GEA and was first verified by the Hall A experiment.
This experiment kinematics moves away from larger recoil angles and focuses on fowards angles at $\theta_{nq}\sim 40^{o}$ where the momentum distributions become accessible. As a result, our data at larger recoil angles
is statistically limited. \\
\indent For recoil angles at $\theta_{nq}=35^{o}$ and $45^{o}$ shown in Figs. \hyperref[fig:fig2]{2(a)}] and  \hyperref[fig:fig2]{2(b)}],  all models predict similar behaviour of the momentum distribution for recoil momenta up to $p_{r}\sim$300 MeV/c which the data verifies. At larger $p_{r}$,
however, the momentum distributions become increasingly sensitive to the NN potentials, mainly a difference between the CD-Bonn and either the Paris or AV18 is observed. \\
\indent In Fig. \hyperref[fig:fig2]{2(a)} for example, the data clearly favors the CD-Bonn momentum distributions between recoil momenta of $300\lesssim p_{r}\lesssim750$ MeV/c before transitioning to the Paris/AV18 potentials which is a behaviour that is not well described by any of the models.
For recoil angles in Fig. \hyperref[fig:fig2]{2(b)}, a similar behaviour can be observed, as the data is sensitive to the CD-Bonn momentum distributions but only up to $p_{r}\sim 580$ MeV/c as FSIs start to dominate at lower $p_{r}$
as opposed to Fig. \hyperref[fig:fig2]{2(a)}. For $p_{r}>580$ MeV/c, the data again exhibits a behaviour at the high momentum tails which either the CD-Bonn, Paris or AV18 potentials are unable to describe.

@@

\begin{figure}[bh!]
\includegraphics[scale=0.5]{prl_plots/PRL_plot1.pdf}
\caption{The reduced cross section $\sigma_{red}(p_{r})$ as a function of neutron recoil momentum $p_{r}$ is shown in (a)-(c) for recoil angles \\  $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively,
with a bin width of $\pm 5^{o}$. The data is compared to the previous Hall A experiment results as well as the Paris, AV18 and CD-Bonn theoretical reduced cross sections.}
\label{fig:fig2}
\end{figure}

\twocolumngrid
\indent We have measured the
